\documentclass[letterpaper,11pt]{article}

\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}

\titleformat{\section}[block]{\normalfont\Large\bfseries}{}{0em}{}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright

\begin{document}
    {\fontsize{15}{20}\selectfont \textbf{Choo Tze Jie}}
    \\
    \faEnvelope\space e0929841@u.nus.edu 
    \faMobile\space 8778 9681
    \faGithub\space \href{https://github.com/tjch-o}{Github} 
    \faLinkedin\space \href{https://www.linkedin.com/in/tze-jie-choo/}{Linkedin}
    \faMapMarker\space Singapore
     
    \section{Education}
    \vspace{-0.5em} 
    \hrule
    \vspace{0.5em}
    \textbf{National University of Singapore} \hfill Aug 2022 - Present
    \\
    Currently pursuing a Bachelor of Computing in Computer Science (with Honours)
    \\
    \vspace{0.5em}
    \textbf{Nanyang Junior College}  \hfill Jan 2018 - Dec 2019
    \\
    Achieved 88.875 rank points in GCE A-Level 
    \\
    \vspace{0.5em}
    \textbf{Zhonghua Secondary School} \hfill Jan 2014 - Dec 2017
    \\
    Achieved raw L1R5 score of 7, net L1R5 score of 3 in GCE O-Level
     
    \section{Certificates}
    \vspace{-0.5em}
    \hrule
    \vspace{0.5em}
    \textbf{Introduction to Machine Learning} 
    \hfill 7 Aug 2023
    \\
    Awarded by Duke University on Coursera
    \\
    \vspace{0.5em}
    \textbf{Foundation Programme in Server, Quality Assurance and Site Reliability Engineering} 
    \hfill 12 Jul 2023
    \\
    Awarded by Tiktok for the 2023 Tiktok Tech Immersion
    \\
    \vspace{0.5em}
    \textbf{Python and Statistics for Financial Analysis} \hfill 9 Jul 2023
    \\
    Awarded by The Hong Kong School University of Science and Technology on Coursera
    \\
    \vspace{0.5em}
    \textbf{Python and Pandas for Data Engineering} \hfill 30 May 2023
    \\
    Awarded by Duke University on Coursera
    \\
    \vspace{0.5em}
    \textbf{Platform Thinking: What's beyond Uber?} \hfill 24 Jan 2023
    \\
    Awarded by Politecnico di Milano on Coursera
     
    \section{Awards and Achievements}
    \vspace{-0.5em}
    \hrule
    \vspace{0.5em}
    NYJC Academic Excellence Award \hfill 2019
    \\
    NYJC Orientation Group Leader \hfill 2019
    \\
    Facilitator for NYJC Experience \hfill 2019
    \\
    Selected as a member for the prestigious NYJC Galileo Programme \hfill 2018 - 2019
    \\
    CDC - CCC Education Merit Award \hfill 2017, 2018
    \\
    SAC Zhonghua Merit Scholarship \hfill 2017
    \\
    Edusave Scholarship \hfill 2015, 2017
    \\
    Top in Class \hfill 2015
    \\
    Merit Award for 10th Singapore Games Creation Competition \hfill 2015
    \\
    2\textsuperscript{nd} place for 50 Years On – Remembering Our Everyday Pioneer Heroes – Digital 
    Story Competition \hfill 2015
    \\
    Silver Award for National Library Board Certificate of Appreciation \hfill 2015
    \\
    MOE Edusave Certificate of Academic Achievement \hfill 2014, 2016, 2018

    \section{Co-curricular Activities (CCA)}
    \vspace{-0.5em}
    \hrule
    \vspace{0.5em}
    \textbf{Photographer for Nanyang Photographic Society} \hfill 2018 - 2019
    \\
    Deployed as a photographer for many events:
    \\
    \vspace{-0.75em}
    \begin{itemize}[itemsep=-0.5em, label=\textbullet]
        \item Class Orientation  \hfill 2019
        \item J2 Dinner and Dance \hfill 2018
        \item CCA Awards \hfill 2018
    \end{itemize}
    \vspace{-0.5em}
    Was also selected as a facilitator for many events: 
    \vspace{-0.75em}
    \begin{itemize}[itemsep=-0.5em, label=\textbullet]
        \item Basic Photography Course  \hfill 2019
        \item CCA Day Camp \hfill 2019
        \item CCA Orientation \hfill 2019
        \item CCA Selection Trials \hfill 2019
    \end{itemize}

    \vspace{0.5em}
    \textbf{Member of ZHSS Infocomm Club} \hfill 2014 - 2017
    \\
    Was chosen as an audio-visual (AV) team leader in 2016 - 2017 and spearheaded the AV system for 
    major school events such as National Day 2016.
    \\
    \vspace{0.5em}
    Actively participated in many competitions:
    \\
    \vspace{-0.75em}
    \begin{itemize}[itemsep=-0.5em, label=\textbullet]
        \item Schools Digital Media Awards  \hfill 2017
        \item Safety With Me Competition (Animation and Short Film) \hfill 2016
        \item Singapore Games Creation Competition \hfill 2015, 2016
        \item Safety Starts With Me Competition \hfill 2014
        \item National Schools Digital Media Competition \hfill 2014
    \end{itemize}

     
    \section{Projects}
    \vspace{-0.5em}
    \hrule
    \vspace{0.5em}
    \textbf{\href {https://github.com/tjch-o/URLShorts}{URLShorts}} \hfill July 2023
    \\
    A URL shortener full stack web app meant to provide short and concise links for long URLs.
    \\
    Frontend uses React.js with Chakra UI and is deployed on Netlify. Backend uses Node.js + 
    Express.js and is hosted on Render. MongoDB Atlas Database is used for the database.

    \vspace{0.5em}
    \textbf{\href {https://github.com/McNaBry/orbital-grindtogether}{GrindTogether}} \hfill May 2023
    - Aug 2023
    \\
    Project for NUS Orbital Programme 2023.
    \\
    A full stack web app that integrates CRUD functionality and allows NUS students to post 
    study invitations based on module, faculty and location. 
    \\
    Frontend uses React.js + Next.js with Bootstrap 5, backend uses Node.js + Express.js with 
    Firebase used for authentication and database. Web app is deployed on Netlify.
     

    \vspace{0.5em}
    \textbf{\href {https://github.com/tjch-o/jeopardy}{Jeopardy}} \hfill May 2023
    \\
    A web app which allows users to play a simple variant of the popular trivia quiz game Jeopardy! 
    anywhere. Users can skip questions as they desire and can click to reveal the answers. The 
    questions are fetched in a random manner from jService API.
    \\
    Developed using React.js and deployed on Netlify.

    \vspace{0.5em}
    \textbf{\href {https://github.com/tjch-o/the-odin-project/tree/main/odin-etch-a-sketch}
    {Etch-A-Sketch}} \hfill Dec 2022
    \\
    A website where users can engage in interactive grid-based drawing and colouring experiences. 
    \\ 
    Developed using HTML 5, CSS and JavaScript.
     
    \section{Skills}
    \vspace{-0.5em}
    \hrule 
    \vspace{0.5em}
    \textbf{Written and spoken languages}:\space English, Chinese

    \vspace{0.5em}
    \textbf{Programming Languages}:\space Python, Java, JavaScript, TypeScript

    \vspace{0.5em}
    \textbf{Frameworks}:\space React.js, Node.js, Express.js, Bootstrap 5, Next.js, Chakra UI

    \vspace{0.5em}
    \textbf{Version Control}:\space Git, Github

    \vspace{0.5em}
    \textbf{Web development}:\space HTML 5, CSS

    \vspace{0.5em}
    \textbf{Database}:\space PostgreSQL, Firebase Realtime Database, MongoDB

    \vspace{0.5em}
    \textbf{Data Analysis and Visualisation}:\space RStudio, Excel, Pandas, NumPy 

    \vspace{0.5em}
    \textbf{Software Testing}:\space Cypress

    \vspace{0.5em}
    \textbf{Deployment}:\space Netlify, Render

\end{document}